---
title: "Homework 1"
author: "Clare Qian"
output: github_document
---

This is my work for P8105 homework 1.

```{r learning_assessment_1, echo=FALSE}
library(tidyverse)
```

##Problem 1

The chunk below creates a data frame.

```{r dataframe}
prob1_df = 
  tibble(
    norm_samp = rnorm(10),
    norm_samp_pos = norm_samp > 0,
    vec_char = c("a", "b", "c", "d","e","f","g","h","i","j"),
    vec_factor = factor(c("low", "low", "low", "mod","mod","mod","mod","high","high","high"))
  )
```

Take the mean of each variable in your dataframe.

```{r mean}
mean(pull(prob1_df, norm_samp))
mean(pull(prob1_df, norm_samp_pos))
mean(pull(prob1_df, vec_char))
mean(pull(prob1_df, vec_factor))
```

I can only take the means of numeric and logical vectors instead of characters or factors.

```{r convert_to_numeric, eval=FALSE}
as.numeric(pull(prob1_df, norm_samp))
as.numeric(pull(prob1_df, norm_samp_pos))
as.numeric(pull(prob1_df, vec_char))
as.numeric(pull(prob1_df, vec_factor))
```

Logical variables can be converted to numbers but characters cannot, so we can take the means of logical variables rather than of characters. However, we can still convert factors to numbers if we insist, but this does not make much sense.

The code chunk below does the conversion and multiplication.

```{r multiply}
as.numeric(pull(prob1_df, norm_samp_pos)) * pull(prob1_df, norm_samp)
as.factor(pull(prob1_df, norm_samp_pos)) * pull(prob1_df, norm_samp)
as.numeric(as.factor(pull(prob1_df, norm_samp_pos))) * pull(prob1_df, norm_samp)
```


##Problem 2

This problem focuses the use of inline R code, plotting, and the behavior of ggplot for variables of different types.

Load the penguins dataset:

```{r load}
data("penguins", package = "palmerpenguins")
```

Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code, including:

The data structure of this dataset:

```{r echo=FALSE}
str(penguins)
```

The dataset includes `r ncol(penguins)` columns and `r nrow(penguins)` rows.

The mean of flipper length is `r mean(pull(penguins,flipper_length_mm),na.rm=TRUE)`.

The chunk below creats a scatterplot.

```{r scatter}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color=species)) + geom_point()
ggsave("prob2plot.pdf")
````